```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
```

```{r}
#read data
data <- read_csv("General/Turkey Covd/covid19-turkey-data.csv")

head(data, 10)
tail(data, 10)
```
```

```{r}
#plotting


plot_1 <- ggplot(data = data, aes(x = date, y = total_case)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) + 
  geom_hline(aes(yintercept = quantile(data$total_case, 0.25, na.rm = TRUE))) +
  geom_hline(aes(yintercept = quantile(data$total_case, 0.5, na.rm = TRUE))) + 
  geom_hline(aes(yintercept = quantile(data$total_case, 0.75, na.rm = TRUE))) +
  labs(
    title = "Total Cases in Turkey",
        subtitle = paste("From March 2020 to November 2020, Variation : ", var(data$total_case) ),
       x = "Date",
       y = "Total Cases"
       )
    

plot_2 <- ggplot(data = data,aes(x = date, y = daily_death)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) + 
  geom_hline(aes(yintercept = quantile(data$daily_death, 0.25, na.rm = TRUE))) +
  geom_hline(aes(yintercept = quantile(data$daily_death, 0.5, na.rm = TRUE))) + 
  geom_hline(aes(yintercept = quantile(data$daily_death, 0.75, na.rm = TRUE))) +
  labs(
    title = "Daily Deaths in Turkey",
    subtitle = "From March 2020 to November 2020",
    x = "Date",
    y = "Daily Deaths",
    )

plot_3 <- ggplot(data = data, aes(x = total_intubated, y = total_case)) +
  geom_point() +
  labs(
    title = "Total Intubated/Cases in Turkey",
    subtitle = "From March 2020 to November 2020",
    x = "Total Intubated",
    y = "Total Cases"
  )

p <- plot_grid(plot_1, plot_2, plot_3, labels = "AUTO", nrow = 3)

ggsave("General/Turkey Covd/plot.PNG", p)

```